A Large-Scale 3D Object Recognition dataset

### 2016-10-02 paper.tex
IJCV template

%%%%%%%%% ABSTRACT
\begin{abstract}
This paper presents a new large scale dataset targeting evaluation of local shape descriptors and 3d object recognition algorithms. The dataset consists of point clouds and triangulated meshes from 292 physical scenes take from 11 different views; a total of approximately 3200 views. Each of the physical scenes contain 10 occluded objects resulting in a dataset with around 32000 unique object poses and 45 different object models. The 45 object models are full 360 degree models which are scanned with a high precision structured light scanner and a turntable. All the included objects belongs to different geometric groups; concave, convex, cylindrical and flat 3D object models. The object models have varying amount of local geometric features to challenge existing local shape feature descriptors in terms of descriptiveness and robustness.  The dataset is validated in a benchmark which evaluates the matching performance of 7 different state-of-the-art local shape descriptors. Further, we validate the dataset in a 3D object recognition pipeline. Our benchmark shows as expected that local shape feature descriptors without any global point relation across the surface have a poor matching performance with flat and cylindrical objects. It is our objective that this dataset contributes to the future development of next generation of 3D object recognition algorithms. The dataset will be made public available.
\end{abstract}

@@

Object recognition in range images is a fundamental research area in computer vision with many different applications in different industries. With the continually introduction of new inexpensive 3D sensors for different applications, the ability to localize and recognize rigid and no rigid objects is an attractive and unavoidable technology. Applications areas such as robotic assembly, bin-picking, mobile robotic manipulation, biometric analysis, tracking and intelligent surveillance all benefits from 3D data for localizing objects. Mainly, because the third dimension is explicit given and not inferred as in 2D object pose estimation. In the last decades many contributions on 2D object recognition and classification have been published, where methods are evaluated on large-scale dataset like the PASCAL Visual Object Challenge (VOC) \cite{Everingham2014} and ImageNet \cite{Imagenet2009}. The benefit from evaluating algorithms on a large-scale dataset has proven valuable in the continues improvement of recognition algorithms after the release of the PASCAL VOC and ImageNet datasets \cite{Everingham2014}.

@@

\indent In this paper we present a new large-scale dataset consisting of 45 objects and 3200 views. The new dataset is recorded systematically in an environment without ambient light and with controlled illumination. The system includes an industrial robot in a dark chamber, a high precision structured light scanner which records data of 292 different scenes from 11 different view points. Each scene consists of 10 occluded objects, automatic taken with the structured light sensor, which results in a dataset with around 32000 unique object poses. With 11 different views of the same scene our dataset is especially suited for studying the effect of view point changes in 3D object recognition. The objects are configured as a classic table-top scenario where different objects are depicted for the side. The dataset is not meant as an evaluation platform for bin-picking and top-view scenarios where many instances of the same object are present in the scene. The table-top scenario is selected because it encapsulate many of the problems and challenges in 3D object recognition in favour of a larger research community.

@@

\indent \textit{Why does the 3D Object recognition community need another dataset?} Previous proposed datasets are limited in the total number of objects, object per. scene and total number of scenes. Additional, the included objects in the different datasets are mostly geometrical ideal objects. With geometrical ideal objects we refers to objects with concave water tight and closed surfaces that are rich of local descriptive geometrical features, like the UWA-chef model \cite{Mian2006},\cite{Mian2010}, the bologna-Armadillo \cite{Salti2014},\cite{Tombari2010} and the Queens-BigBird \cite{Taati2007},\cite{Taati2007}. In our dataset we include not only ideal concave objects, but flat, cylindrical, feature-rich, simple concave and convex objects. It is expected that some local shape features will have a poor performance on our dataset because the lack of local geometric features. However, our main goal for proposing this dataset is to highlight the challenges in 3D object recognition research and strengthen the data foundation in future algorithm development. This work is initiated because of previous experiences on pose estimation of geometric simple objects in an industrial robotic context. We hope that new novel methods for 3D object recognition will emerge in the future as a side-effect of this dataset. Not only local shape descriptos but to a great extend features that uses point relations across the surface e.g. Point Pair Features \cite{BirdalIlic2015}, semi-global features and template matching.    
We have selected the different objects based on previous experience, as a combination of lab-objects and industrial objects. The industrial objects are provided by companies that wish to pick the objects from boxes or bins with a robot. Thus, the dataset is a mix of objects that we know is problematic and objects from our lab which are more suited for in a 3D object recognition pipeline with local shape features.\\

@@

             Queens Lidar  \cite{Taati2011}, \cite{Taati2007}  & 5 & 80 & LIDAR & (1-5)/(1-5) & \checkmark  & \checkmark & \%  & 0 & \checkmark & \% & \% & R\\

@@

             Queens Stereo  \cite{Taati2011}, \cite{Taati2007}  & 5 & 100 & Stereo & (3)/(3)   & \checkmark & \checkmark & \%  & 0 & \checkmark & \% & \% & R\\

@@

             Vienna Kinect \cite{Aldoma2012} & 35 & 50 & Kinect V1 & 0 & \checkmark & \checkmark & \% & 0 & \checkmark & \% & \% & R\\

@@

             RGB-D Scenes V1 \cite{Lai2011}, \cite{Lai2012} & 5 & 8 videos & Kinect V1 & (0)/ & \% & \%  & \%  & \% & \% & \% & \% & R\\

@@

             RGB-D Scenes V2 \cite{Lai2014} & 9 & 14 & Kinect V1 & (0)/ & \% & \% & \% & \% & \% & \% & \% & R\\

@@

             Willow \cite{Willow} & 35 & 177 & Kinect V1 & 0 & \checkmark  & \checkmark  & \% & 0 & \% & \% & \% & R\\

@@

              Alicante \cite{Garcia-Garcia2016}  & 30 & 50 & Kinect V2 & (0)/(0) & \% & \checkmark  & \% & 0 & \checkmark & \% & \% & R\\

@@

             \textbf{Our dataset}  & \textbf{45} & \textbf{3200} & SL & (10)/(10) & \checkmark  & \checkmark  & \checkmark & \checkmark & \checkmark  & \checkmark & \checkmark & R\\

@@

\caption{Comparison of existing datasets for 3D object recognition with the presented datasets. {$M_q$} is the amount of different models in the dataset and {$S_t$} is the amount of scenes.[R]/[S] indicates whether the dataset is synthetic or acquired in real world. }

@@

\noindent
\textbf{3D Object Recognition datasets:}\\
The last 10 years a few 3D object recognition datasets have been published. Mainly in conjunction with algorithms for local feature description \cite{Mian2006},\cite{Taati2007},\cite{Taati2011},\cite{Tombari2010},\cite{Salti2014}, correspondence matching and rejection \cite{Rodola2013}, pose hypothesis verification \cite{Aldoma2012} and 3D keypoint detection \cite{Mian2010}. Common for all existing dataset are the limited number of 3D object models and scenes. A comparison of the different datasets are presented in Table \ref{tab:dataset_overview}. The most common used datasets are the UWA  \cite{Mian2006}, \cite{Mian2010}, Queens \cite{Taati2007},\cite{Taati2011} and the Bologna \cite{Salti2014}, \cite{Tombari2010}. These datasets are widely used in performance evaluations of  local feature descriptors \cite{Guo2015}, \cite{Buch2016}, keypoint detectors \cite{Salti2011} and surveys \cite{Guo2014}, \cite{FilipeAlexandre2014}. The main problems of all the datasets are; size, variety of objects, few objects per. scene and missing occlusion/clutter estimates. For object recognition in 2.5D, where either a full object model or sampled templates are used for recognizing object in a color and depth image, is not considered in this work. However, some datasets exist for this problem e.g. the Line-Mod dataset \cite{Hinterstoisser2012}.\\

\noindent
\textbf{Local feature descriptors:}\\
During the last three decades, a vast number of different 3D local feature descriptors have been proposed including SPLASH \cite{Stein1992}, Spin Image (SI) \cite{Johnson1999}, 3D Shape Context (3DSC) \cite{Frome2004}, LSP \cite{ChenBhanu2004}, 3D Tensors \cite{Mian2006}, THRIFT \cite{Flint2007}, MESH-HOG \cite{Zaharescu2009}, ISS \cite{Zhong2009}, Unique shape context (USC) \cite{usc2010}, Point Feature Histogram (PFH) \cite{Rusu2008}, Fast Point Feature Histograms (FPFH) \cite{Fpfh2009}, SHOT \cite{Tombari2010}, ROPS \cite{Guo2013}, ECSAD \cite{Ecsad2015} and Tri-Spin-Image (TriSI)\cite{Guo2015}. The descriptors find usages in applications such as 3D object categorization, recognition, retrieval, analysis, registration and reconstruction among others. Designing descriptors which are distinctive and robust to occlusion and noise is still an ongoing research topic.

@@

Recent studies have shown that the state of the art features are not generalizing well over many types of geometry classes, \cite{Guo2015},\cite{Buch2016}. The studies proved one of the main issues in 3D object recognition today, namely the fact that there exist no local shape feature that describes the geometry well over many different object classes, e.g. flat, rotational symmetrical and geometrically feature rich objects. What feature(s) to use are still dependent on the object geometry. However, the experimental result in \cite{Buch2016} showed the advantage of fusing several local feature descriptors. 
The studies from \cite{Guo2015},\cite{Buch2016} leave a relevant research question to be answered; are the local feature descriptors not descriptive enough to generalize over different object classes or are the data used for evaluation too limited? The evaluation datasets used for the evaluation in general and in \cite{Guo2015},\cite{Buch2016} consist mainly of objects with many descriptive and distinctive geometrical features.\\ 

@@

We have constructed a dataset by achieving highly accurate 3D model of each of the 45 individual objects, as described in Section \ref{sec:object_scanning}. These are then used to compose 292 individual scenes where 10 objects are placed in different configurations. A robot moves our scanner to 11 fixed positions in order to create 11 independent view points of the same object configuration, as described in Section \ref{sec:scene_scanning}. Hence, we have 3200 individual observations of 10 objects included in the dataset. We argue that these observations are independent because of the large view point change at 36 degree horizontal and 45 degree vertical. Thus, the objects surface are very different in each view. We achieve very accurate ground truth poses by annotating the entire dataset with our high resolution object models in full resolution, as described in Section \ref{sec:gt_pose}. 

@@

a high resolution DLP projector (LG PF80G) mounted on a rigid aluminium frame. In addition, a high precision turntable (Newmark Systems RT-5) is used in order to provide automatic rotation of the object. Each of the 45 objects are incremental scanned with a rotation of 20 degrees. 

@@

All individual scan views are reconstructed by the Line shifting algorithm \cite{Guehring2000} which results in accurate and dense point cloud of the objects. Eleven temporal binary gray code patterns are projected followed by eight line shifting patterns. The point resolution of the scanned objects are in average 275 microns and consist of around 908000 vertices and 1.8 million faces in average. Once a single view of the model is scanned, noisy outliers of the measurement are manual removed and surface normals are estimated to ensure consistent normals. All 18 views are registered with Iterative Closest Point (ICP) and a new object frame is computed with principal component analysis on the point set. All models are sampled with a Poisson disk sampling algorithm \cite{Corsini2012} and triangulated with the poisson reconstruction algorithm \cite{Kazhdan2006} with an octree depth=14, solver divide = 8 and iso divide = 5. We use the PCL implementation \cite{RusuCousins2011}. All models are provided as coloured point clouds and triangular meshes, all in the $.ply$ format, see Figure \ref{fig:objects}. Note that the modelling setup is not radiometrical calibrated.

@@

\caption{Example on one of the 3200 triangulated scene}

@@

For each of the 3200 scenes the 6D ground truth pose, occlusion and clutter estimates for each object are provided. We estimate the occlusion from Equation \ref{eq:occlusion} and clutter from Equation \ref{eq:clutter} by counting the number of points at the object model in which the squared euclidean distance to a scene point is less than two times the scene resolution. Both the object model and the scene are sampled to ensure equal point distance.

@@

Accurate ground true poses are ensured by manual annotation of each object in the scenes. First, one point cloud that covers 180 degree of the scene is stitched together form each of the 11 views and registered with ICP. This full scene point cloud is applied in the annotation process, see Figure \ref{fig:scene}. The full scene point cloud covers the geometric structures of each model in the scene with more point compared to the individual views. Thus, it is possible to get a more accurate ICP registration of the object model in the scenes. All 290 combined scenes are manual annotated by selecting four identical points for each model and the scene, followed by an estimation of the rigid transform. An iterative ICP, which incremental decreases the allowed correspondence distance ensures a very accurate final ground truth pose of each object in the scene. The final ICP iterations are accomplished with the full resolution model to get the best fit of the model points to the scene points. The individual ground truth poses in each sensor view $T_{sensor_{n}}$ is computed by transforming the ground truth poses from the world frame $T_{world}$ to each of the individual sensor frames $T_{sensor_{n}}$. Equation \ref{eq:transformation} show the final transformation. 

@@

The descriptiveness and accuracy of a feature descriptor are measured with Precision-Recall and presented as 1-Precision vs. Recall Cruves (PRC). First we sample both the query models and the target scenes with a voxel grid sampling \cite{RusuCousins2011} which results in equal point distance. The voxel size is tuned to give approximately 1000 seed points per. object in both the query and target. The target seed points are found by transforming the query seeds into the target by applying the object ground truth pose. The target seeds are selected in a nearest neighbour search with a distance threshold. A feature descriptor for each seed point in the query and target mesh is computed.  For fair comparison individually tuned support radii for each descriptors are used. We use the following feature resolution multiplier: SI($20$), 3DSC($22.5$), FPFH($17.5$), USC($25$), SHOT($17.5$), ROPS($20$), ECSAD($20$), NDHIST($31$). Hence, the radius for each feature is a function of the average model or scene resolution. Upon feature computation the underlying scene and object meshes are utilized in 0.25 and 0.05 decimated version; respectively. The level of decimation are empirical determined to the level with best overall matching results for all features. During decimation the normal orientation is re-computed for each vertex by the area weighted mean of the mesh triangle \cite{Thurmer1998} and normalized. In order to resolve the exact number of correct feature matches, a brute-force linear kd-tree search is	 used with a ${L_2}$ distance function. Other distance metrics such as ${L_1}$, ${L_\infty}$, are tested in previous work but the best results are achieved with the $L_2$ distance metric. Thus, we only present results for the ${L_2}$ metric. During matching we are computing the ratio of the nearest and the second-nearest matching distances. This matching strategy is adapted from multiple previous studies e.g. Lowe \etal \cite{Lowe2004} that proved a performance enhancement compared to a native matching strategy where only the nearest neighbour is considered. 

@@

In this section the experimental protocol for the pose estimation experiments is presented. The sampling and seed point selection are identical with the feature matching benchmark presented, except that we cannot use the ground truth pose for selecting target seed points. Instead, the target resolution is doubled, to quadruples the number of feature descriptors which increase the chance for describing the same feature. To increase the efficiency during matching we apply approximate nearest neighbour search to determine correspondences hypotheses instead of exact matching. Again, the ratio of the nearest and second nearest neighbours feature distances are used. A multiple randomized kd-trees with a bound of 512 checks and 4 trees are used as a good trade-off between accuracy and efficiency. Correspondences are ranked by the ${L_2}$ distance which inputs potential feature correspondences to a hypothesis and test RANSAC algorithm.

@@

In this section we present the results of our evaluation benchmark. All experiments are based on the proposed dataset where 3204 scenes, 45 objects and 5675 ground truth poses are included. As a first evaluation we benchmark the matching accuracy of the seven feature descriptors with the parameters outlined in Section \ref{sec:benchmark_matching} and all 45 object models included. The PRC curve of the overall matching accuracy is presented in Figure \ref{fig:all_L2_RATIO_zoom}.   

@@

As expected the total matching accuracy is much lower compared to previous studies e.g. Guo \etal \cite{Guo2015} and Buch \etal \cite{Buch2016}, which both are running a similar benchmark but on previous proposed datasets. The result indicate that our objective of the proposed dataset has been fulfilled. Moreover, the evaluation shows that the ECSAD feature has a best performance with a AUC = 0.046 followed by ROPS with AUC = 0.011. In order to investigate the performance further we run the matching benchmark for each object model and compute PRC curves for each of the 45 models. We have categorize the object into three different groups and present 3 PRC curves for each group in Figure \ref{fig:angel}-\ref{fig:noise} as a sample. The three groups are a) Geometric complex objects, b) Cylindrical objects and c) Flat or box shaped objects. The objects that corresponds to the PRC curves in Figure \ref{fig:angel}-\ref{fig:noise} are presented in Figure \ref{fig:selected_objects}. The geometric complex objects are the Angel, the Birds and the Rabbit in Figure \ref{fig:selected_objects}(a)-(c), the cylindrical objects are Neutral, Pringles and Hand soap in Figure \ref{fig:selected_objects}(d)-(f), and the flat or box shaped objects are the button, the brake disc and the Psu in Figure \ref{fig:selected_objects}(g)-(i). The results show that a recent precision and recall are achieved with the Angel,Birds and Rabbit, but it is much lower than previous studies e.g. Buch \etal \cite{Buch2016} that obtain very matching accuracy for some datasets. These low numbers for our geometric ideal objects indicate that the proposed dataset have the desired level of complexity.     Regarding, the cylindrical objects which features the Neutral, Pringles and Hand Soap objects, it is clear that current local shape descriptors is very little descriptive for these uniform shaped objects. Again, ECSAD performs in general best which might results from the fact that ECSAD describes edges in a good way. For the flat and boxed shaped models we can conclude that current state of the art feature descriptors is not suitable as the only detection method.\\ 	
\indent The result for the pose estimation experiments are presented in Table \ref{tab:recognition} and Figure \ref{fig:pose_est_results}. Our object recognition pipeline in these experiment is in accordance to the presented pipeline in Section \ref{sec:pose_estimation}. 

@@

\scalebox{0.8}{
\begin{tabular}{p{1.25cm} | P{1.1cm} | P{1.4cm} P{1.4cm} P{1.4cm} P{1.4cm} P{1.4cm} P{1.7cm} P{1.4cm} P{1.65cm} P{1.4cm} | P{1.4cm}}

@@

\caption{Qualitative recognition results for scene 8}\label{fig:pose_est_results}

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
This paper presents a new large scale dataset targeting evaluation of local shape descriptors and 3d object recognition algorithms. The dataset consists of point clouds and triangulated meshes from 292 physical scenes taken from 11 different views; a total of approximately 3204 views. Each of the physical scenes contain 10 occluded objects resulting in a dataset with 32040 unique object poses and 45 different object models. The 45 object models are full 360 degree models which are scanned with a high precision structured light scanner and a turntable. All the included objects belong to different geometric groups; concave, convex, cylindrical and flat 3D object models. The object models have varying amount of local geometric features to challenge existing local shape feature descriptors in terms of descriptiveness and robustness.  The dataset is validated in a benchmark which evaluates the matching performance of 7 different state-of-the-art local shape descriptors. Further, we validate the dataset in a 3D object recognition pipeline. Our benchmark shows as expected that local shape feature descriptors without any global point relation across the surface have a poor matching performance with flat and cylindrical objects. It is our objective that this dataset contributes to the future development of next generation of 3D object recognition algorithms. The dataset will be made public available together with this paper.
\end{abstract}

@@

Object recognition from range images is a fundamental research area in computer vision with many different applications in different industries. With the continually introduction of new inexpensive 3D sensors for different applications, the ability to localize and recognize rigid and no rigid objects is an attractive and unavoidable technology. Applications areas such as robotic assembly, bin-picking, mobile robotic manipulation, biometric analysis, tracking and intelligent surveillance all benefits from 3D data for localizing objects. Mainly, because the third dimension is explicit given and not inferred as in 2D object pose estimation. In the last decades many contributions on 2D object recognition and classification have been published, where methods are evaluated on large-scale dataset like the PASCAL Visual Object Challenge (VOC) \cite{Everingham2014} and ImageNet \cite{Imagenet2009}. The benefit from evaluating algorithms on a large-scale dataset has proven valuable in the continues improvement of recognition algorithms after the release of the PASCAL VOC and ImageNet datasets \cite{Everingham2014}.

@@

\indent In this paper we present a new large-scale dataset consisting of 45 objects and 3204 views. The new dataset is recorded systematically in an environment without ambient light and with controlled illumination. The system includes an industrial robot in a dark chamber, a high precision structured light scanner which records data of 292 different scenes from 11 different view points. Each scene consists of 10 occluded objects, automatically taken with a structured light sensor, which results in a dataset with 32040 unique object poses. With 11 different views of the same scene our dataset is especially suited for studying the effect of view point changes in 3D object recognition. The objects are configured as a classic table-top scenario where different objects are depicted form the side. The dataset is not meant as an evaluation platform for bin-picking and top-view scenarios where many instances of the same object are present in the scene. The table-top scenario is selected because it encapsulates many of the problems and challenges in 3D object recognition in favour of a larger research community.

@@

\indent \textit{Why does the 3D Object recognition community need another dataset?} Previous proposed datasets are limited in the total number of objects, object per. scene and total number of scenes. Additional, the included objects in the different datasets are mostly geometrical ideal objects. With geometrical ideal objects we refer to objects with concave water tight and closed surfaces that are rich of local descriptive geometrical features, like the UWA-chef model \cite{Mian2006},\cite{Mian2010}, the bologna-Armadillo \cite{Salti2014},\cite{Tombari2010} and the Queens-BigBird \cite{Taati2007},\cite{Taati2007}. In our dataset we include not only ideal concave objects, but flat, cylindrical, feature-rich, simple concave and convex objects. It is expected that some local shape features will have a poor performance on our dataset because the lack of local geometric features. However, our main goal for proposing this dataset is to highlight the challenges in 3D object recognition research and strengthen the data foundation in future algorithm development. This work is initiated by our previous experiences on pose estimation of geometric simple objects in an industrial robotic context. We hope that new novel methods for 3D object recognition will emerge in the future, as a side-effect of this dataset. Not only local shape descriptors but to a great extend features that use point relations across the surface e.g. Point Pair Features \cite{BirdalIlic2015}, semi-global features and template matching.    
We have selected the different objects based on previous experience, as a combination of lab-objects and industrial objects. The industrial objects are provided by companies that need to pick the objects from boxes or bins with a robot. Thus, the dataset is a mix of real industrial objects that we know from experience is difficult to detect and objects from our lab which are more suited for a 3D object recognition pipeline with local shape features.\\

@@

             Queens Lidar  \cite{Taati2011}, \cite{Taati2007}  & 5 & 80 & LIDAR & (1-5)/(1-5) & \checkmark  & \checkmark & \%  & \checkmark & \checkmark & \% & \% & R\\

@@

             Queens Stereo  \cite{Taati2011}, \cite{Taati2007}  & 5 & 100 & Stereo & (3)/(3)   & \checkmark & \checkmark & \%  & \checkmark & \checkmark & \% & \% & R\\

@@

             Vienna Kinect \cite{Aldoma2012} & 35 & 50 & Kinect V1 & (1-5)/(1-5) & \checkmark & \checkmark & \% & \% & \checkmark & \% & \% & R\\

@@

             RGB-D Scenes V1 \cite{Lai2011}, \cite{Lai2012} & 5 & 8 videos & Kinect V1 & (0)/(5) & \% & \%  & \%  & \% & \% & \% & \% & R\\

@@

             RGB-D Scenes V2 \cite{Lai2014} & 9 & 14 & Kinect V1 & (0)/(9) & \% & \% & \% & \% & \% & \% & \% & R\\

@@

             Willow \cite{Willow} & 35 & 177 & Kinect V1 & * & \checkmark  & \checkmark  & \% & \% & \% & \% & \% & R\\

@@

              Alicante \cite{Garcia-Garcia2016}  & 28 & 9 & Kinect V2 & * & \% & \checkmark  & \% & 0 & \checkmark & \% & \% & R\\

@@

             \textbf{Our dataset}  & \textbf{45} & \textbf{3204} & SL & (10)/(10) & \checkmark  & \checkmark  & \checkmark & \checkmark & \checkmark  & \checkmark & \checkmark & R\\

@@

\caption{Comparison of existing datasets for 3D object recognition with the presented datasets. {$M_q$} is the amount of different models in the dataset and {$S_t$} is the amount of scenes. {$M_q$} in {$S_t$} shows how many models annotated in each scene and how many objects there are in each scene (No. annotated in scene/No. of object in scene).[R]/[S] indicates whether the dataset is synthetic or acquired in the real world. \textit{(* dataset unavailable online)}}

@@

\noindent
\textbf{3D Object Recognition datasets:}\\
The last 10 years a few 3D object recognition datasets have been published. Mainly in conjunction with algorithms for local feature description \cite{Mian2006},\cite{Taati2007},\cite{Taati2011},\cite{Tombari2010},\cite{Salti2014}, correspondence matching and rejection \cite{Rodola2013}, pose hypothesis verification \cite{Aldoma2012} and 3D keypoint detection \cite{Mian2010}. Common for all existing dataset are the limited number of 3D object models and scenes. A comparison of the different datasets are presented in Table \ref{tab:dataset_overview}, from which it is seen that our dataset is magnitudes larger. The most common used datasets are the UWA  \cite{Mian2006}, \cite{Mian2010}, Queens \cite{Taati2007},\cite{Taati2011} and the Bologna \cite{Salti2014}, \cite{Tombari2010}. These datasets are widely used in performance evaluations of  local feature descriptors \cite{Guo2015}, \cite{Buch2016}, keypoint detectors \cite{Salti2011} and surveys \cite{Guo2014}, \cite{FilipeAlexandre2014}. The main problems of all the datasets are; size, variety of objects, few objects per. scene and missing occlusion/clutter estimates. 
In this work we are not considering 2.5D recognition methods where either a full object model or sampled templates is used for recognizing object in a RGB-D image. However, some datasets exist for this problem e.g. the Line-Mod dataset \cite{Hinterstoisser2012} or the recent published RGB-D dataset for warehouse pick-and-place tasks \cite{Rennie2015}.\\

\noindent
\textbf{Local feature descriptors:}\\
During the last three decades, a vast number of different 3D local feature descriptors have been proposed including SPLASH \cite{Stein1992}, Spin Image (SI) \cite{Johnson1999}, 3D Shape Context (3DSC) \cite{Frome2004}, LSP \cite{ChenBhanu2004}, 3D Tensors \cite{Mian2006}, THRIFT \cite{Flint2007}, MESH-HOG \cite{Zaharescu2009}, ISS \cite{Zhong2009}, Unique shape context (USC) \cite{usc2010}, Point Feature Histogram (PFH) \cite{Rusu2008}, Fast Point Feature Histograms (FPFH) \cite{Fpfh2009}, SHOT \cite{Tombari2010}, ROPS \cite{Guo2013}, ECSAD \cite{Ecsad2015} and Tri-Spin-Image (TriSI)\cite{Guo2015}. The descriptors find usages in applications such as 3D object categorization, recognition, retrieval, analysis, registration and reconstruction among others. Designing descriptors which are distinctive and robust toward occlusion and noise is still an ongoing research topic.

@@

Recent studies have shown that the state of the art features are not generalizing well over many types of geometry classes, \cite{Guo2015},\cite{Buch2016}. The studies proved one of the main issues in 3D object recognition today, that there exist no local shape feature which describes the geometry well over many different object classes, e.g. flat, rotational symmetrical and geometrically feature rich objects. What feature(s) to use are still dependent on the object geometry. However, the experimental results in \cite{Buch2016} showed the advantage of fusing several local feature descriptors. 
The studies from \cite{Guo2015},\cite{Buch2016} leave a relevant research question to be answered; are the local feature descriptors not descriptive enough to generalize different object classes or are the data used for evaluation too limited? The evaluation datasets used for the evaluation in general and in \cite{Guo2015},\cite{Buch2016} consist mainly of objects with many descriptive and distinctive geometrical features.\\ 

@@

We have constructed a dataset by achieving highly accurate 3D model of each of the 45 individual objects, as described in Section \ref{sec:object_scanning}. These are then used to compose 292 individual scenes where 10 objects are placed in different configurations. A robot moves our scanner to 11 fixed positions in order to create 11 independent view points of the same object configuration, as described in Section \ref{sec:scene_scanning}. Hence, we have 3204 individual observations of 10 objects included in the dataset. We argue that these observations are independent because of the large view point change at 36 degree horizontal and 45 degree vertical. Thus, the objects surface are very different in each view. We achieve very accurate ground truth poses by annotating the entire dataset with our high resolution object models in full resolution, as described in Section \ref{sec:gt_pose}. 

@@

a high resolution DLP projector (LG PF80G) mounted on a rigid aluminium frame. 

@@

In addition, a high precision turntable (Newmark Systems RT-5) is used in order to provide automatic rotation of the object. Each of the 45 objects are incremental scanned with a rotation of 20 degrees. All individual scan views are reconstructed by the Line shifting algorithm \cite{Guehring2000}, which results in accurate and dense point clouds of the objects. Eleven temporal binary gray code patterns are projected followed by eight line shifting patterns. The point resolution of the scanned objects are in average 275 microns and consist of around 908000 vertices and 1.8 million faces in average. Once a single view of the model is scanned, noisy outliers of the measurement are manual removed and surface normals are estimated to ensure consistent normals. All 18 views are registered with Iterative Closest Point (ICP) and a new object frame is computed with principal component analysis on the point set. All models are sampled with a Poisson disk sampling algorithm \cite{Corsini2012} and triangulated with the poisson reconstruction algorithm \cite{Kazhdan2006} with an octree depth=14, solver divide = 8 and iso divide = 5. We use the PCL implementation \cite{RusuCousins2011}. All models are provided as coloured point clouds and triangular meshes, all in the $.ply$ format, see Figure \ref{fig:objects}. Note that the modelling setup is not radiometrical calibrated.

@@

\caption{Example on one of the 3204 triangulated scene}

@@

For each of the 3204 scenes the 6D ground truth pose, occlusion and clutter estimates for each object are provided. We estimate the occlusion from Equation \ref{eq:occlusion} and clutter from Equation \ref{eq:clutter} by counting the number of points at the object model in which the squared euclidean distance to a scene point is less than two times the scene resolution. Both the object model and the scene are sampled to ensure equal point distance.

@@

Accurate ground true poses are ensured by manual annotation of each object in the scenes. First, one point cloud that covers 180 degree of the scene is stitched together form each of the 11 views and registered with ICP. This full scene point cloud is applied in the annotation process, see Figure \ref{fig:scene}. The full scene point cloud covers the geometric structures of each model in the scene with more points compared to the individual views. Thus, it is possible to get a more accurate ICP registration of the object model in the scenes. All 290 combined scenes are manually annotated by selecting four identical points for each model and the scene, followed by an estimation of the rigid transform. An iterative ICP, which incremental decreases the allowed correspondence distance ensures a very accurate final ground truth pose of each object in the scene. The final ICP iterations are accomplished with the full resolution model to get the best fit of the model points to the scene points. The individual ground truth poses in each sensor view $T_{sensor_{n}}$ is computed by transforming the ground truth poses from the world frame $T_{world}$ to each of the individual sensor frames $T_{sensor_{n}}$. Equation \ref{eq:transformation} shows the final transformation. 

@@

The descriptiveness and accuracy of a feature descriptor are measured with Precision-Recall and presented as 1-Precision vs. Recall Cruves (PRC). First we sample both the query models and the target scenes with a voxel grid sampling \cite{RusuCousins2011} which results in equal point distance. The voxel size is tuned to give approximately 1000 seed points per. object in both the query and target. The target seed points are found by transforming the query seeds into the target by applying the object ground truth pose. The target seeds are selected in a nearest neighbour search with a distance threshold. A feature descriptor for each seed point in the query and target mesh is computed.  For a fair comparison individually tuned support radii for each descriptors are used. We use the following feature resolution multiplier: SI($20$), 3DSC($22.5$), FPFH($17.5$), USC($25$), SHOT($17.5$), ROPS($20$), ECSAD($20$), NDHIST($31$). Hence, the radius for each feature is a function of the average model or scene resolution. Upon feature computation the underlying scene and object meshes are utilized in 0.25 and 0.05 decimated version; respectively. The level of decimation are empirical determined to the level with best overall matching results for all features. During decimation the normal orientation is re-computed for each vertex by the area weighted mean of the mesh triangle \cite{Thurmer1998} and normalized. In order to resolve the exact number of correct feature matches, a brute-force linear kd-tree search is	 used with a ${L_2}$ distance function. Other distance metrics such as ${L_1}$, ${L_\infty}$, are tested in previous work but the best results are achieved with the $L_2$ distance metric. Thus, we only present results for the ${L_2}$ metric. During matching we are computing the ratio of the nearest and the second-nearest matching distances. This matching strategy is adapted from multiple previous studies e.g. Lowe \etal \cite{Lowe2004} that proved a performance enhancement compared to a native matching strategy where only the nearest neighbour is considered. 

@@

In this section the experimental protocol for the pose estimation experiments is presented. The sampling and seed point selection are identical with the feature matching benchmark presented, except that we cannot use the ground truth pose for selecting target seed points. Instead, the target resolution is doubled, thus quadrupling the number of feature descriptors which increase the chance for describing the same feature. To increase the efficiency during matching we apply approximate nearest neighbour search to determine correspondences hypotheses instead of exact matching. Again, the ratio of the nearest and second nearest neighbour feature distances are used. A multiple randomized kd-trees with a bound of 512 checks and 4 trees are used as a good trade-off between accuracy and efficiency. Correspondences are ranked by the ${L_2}$ distance which inputs potential feature correspondences to a hypothesis and test RANSAC algorithm.

@@

In this section we present the results of our evaluation benchmark. All experiments are based on the proposed dataset where 3204 views, 45 objects and 5675 ground truth poses are included. As a first evaluation we benchmark the matching accuracy of the seven feature descriptors with the parameters outlined in Section \ref{sec:benchmark_matching} and all 45 object models included. The PRC curve of the overall matching accuracy is presented in Figure \ref{fig:all_L2_RATIO_zoom}.   

@@

As expected the total matching accuracy is much lower compared to previous studies e.g. Guo \etal \cite{Guo2015} and Buch \etal \cite{Buch2016}, where both are running a similar benchmark but on previous proposed datasets. The result indicates that our objective of the proposed dataset has been fulfilled. Moreover, the evaluation shows that the ECSAD feature has a best performance with a AUC = 0.046 followed by ROPS with AUC = 0.011. In order to investigate the performance further we run the matching benchmark for each object model and compute PRC curves for each of the 45 models. We have categorize the object into three different groups and present 3 PRC curves for each group in Figure \ref{fig:angel}-\ref{fig:noise} as a sample. The three groups are a) Geometric complex objects, b) Cylindrical objects and c) Flat or box shaped objects. The objects that corresponds to the PRC curves in Figure \ref{fig:angel}-\ref{fig:noise} are presented in Figure \ref{fig:selected_objects}. The geometric complex objects are the Angel, the Birds and the Rabbit in Figure \ref{fig:selected_objects}(a)-(c), the cylindrical objects are Neutral, Pringles and Hand soap in Figure \ref{fig:selected_objects}(d)-(f), and the flat or box shaped objects are the button, the brake disc and the Psu in Figure \ref{fig:selected_objects}(g)-(i). The results show that a recent precision/recall is achieved with the Angel,Birds and Rabbit, but it is much lower than previous studies e.g. Buch \etal \cite{Buch2016} who obtain very matching accuracy for some datasets. These low numbers for our geometric ideal objects indicate that the our dataset has the desired level of complexity. Regarding, the cylindrical objects which features the Neutral, Pringles and Hand Soap objects, it is clear that current local shape descriptors are very little descriptive for these uniform shaped objects. Again, ECSAD performs in general best which might results from ECSAD' ability to capture edges. For the flat and boxed shaped models we can conclude that current state of the art feature descriptors is not suitable as the only detection method.\\ 	
\indent The results for the pose estimation experiments are presented in Table \ref{tab:recognition} and Figure \ref{fig:pose_est_results}. Our object recognition pipeline in these experiment is in accordance to the presented pipeline in Section \ref{sec:pose_estimation}. 

@@

\scalebox{0.78}{
\begin{tabular}{p{1.25cm} | P{1.1cm} | P{1.4cm} P{1.4cm} P{1.4cm} | P{1.4cm} P{1.4cm} P{1.7cm} | P{1.4cm} P{1.65cm} P{1.4cm} | P{1.4cm}}

@@

\caption{Qualitative recognition results for view 94}\label{fig:pose_est_results}
